\documentclass{article}

% Language setting
% Replace `english' with e.g. `spanish' to change the document language
\usepackage[english]{babel}

% Set page size and margins
% Replace `letterpaper' with`a4paper' for UK/EU standard size
\usepackage[letterpaper,top=2cm,bottom=2cm,left=3cm,right=3cm,marginparwidth=1.75cm]{geometry}

% Useful packages
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage[colorlinks=true, allcolors=blue]{hyperref}

\title{Combinatorical analysis of burst failures for large-scale cluster}
\author{Meng Wang}

\begin{document}
\maketitle

\section{Setup}
We consider a storage system of N drives such that $N = X \cdot Y \cdot Z$, where there are $X$ racks in the system, each rack contains $Y$ enclosures, and each enclosure contains $Z$ drives.

Let $M = Y \cdot Z$, so $M$ denotes the number of drives per rack.

In particular, we are considering ORNL Alpine system, which is composed of 39 racks. 38 racks have 8 enclosures each, and 1 rack has 4 enclosures. Each enclosure has 106 drives.

For simplicity, we assume the system contains 40 racks. Each rack contains 8 enclosures. Each enclosure contains 100 drives.

\section{Total instances with fixed number of affected racks}

Consider $f$ failures happen in $r$ racks.

We first choose $r$ racks from all the $X$ racks, which has $C_{X}^{r}$ combinations.

Given $r$ racks $1,2,...,r$, denote $T(f,r)$ as the total number of instances for $f$ failures to happen in $r$ racks, such that each rack has at least one failure.

Consider the $r$-th rack. If it has $i$ failures, then the rest $r-1$ racks must have $(f-i)$ failures in total with each rack having at least one failure.

Therefore, we have the following recurrence relation:

\begin{eqnarray}
\begin{aligned}
  T(f,r)
  &= \sum_{\substack{1 \leq i \leq f \\ i \leq M}} C_M^i \cdot T(f-i, r-1)
\end{aligned}
\label{eq:total:rec}
\end{eqnarray}

The base case is 

\begin{eqnarray}
  T(f,1) =
    \begin{cases}
      C_M^f& \text{if $1 \leq f \leq M$}\\
      0 & \text{otherwise}
    \end{cases}       
\label{eq:total:base}
\end{eqnarray}

Therefore, we can compute $T(f,r)$ using dynamic programming, with time complexity $O(f \cdot r)$, and memory complexity $O(f \cdot r)$. An implementation can be found at: \url{https://github.com/ucare-uchicago/mlec-sim/blob/main/src/theory/burst_theory.py#L30}

The total number of instances is:
\begin{eqnarray}
  C_{X}^{r} \cdot T(f,r)
\label{eq:total:final}
\end{eqnarray}

\section{Survival instances under local clustered (RAID)}\label{sec-raid}

Consider $k_l+p_l$ local-only RAID SLEC. For easier deployment we assume $n_l=k_l+p_l$ is divisible by Z.

$n_l$ drives in the same enclosure compose a RAID disk group. Therefore a rack contains $g = M/n_l$ RAID groups.

Denote $\eta(f, g)$ as the number of instances for one single rack to survive $f$ failures in a rack containing $g$ $k_l+p_l$ RAID groups.

For $\eta(f, g)$, we have the following recurrence relation (which is derived by considering what will happen if $g$-th group contains $i$ failures):

\begin{eqnarray}
\begin{aligned}
  \eta(f, g) &= \sum_{\substack{0 \leq i \leq p_l \\ a\leq f}} \eta(f-i, g-1) \cdot C_{n_l}^i
\end{aligned}
\label{eq:raid:1}
\end{eqnarray}

The base case is 

\begin{eqnarray}
  \eta(f, 1) =
    \begin{cases}
      C_{n_l}^f& \text{if $0 \leq f \leq n_l$}\\
      0 & \text{otherwise}
    \end{cases}       
\label{eq:raid:2}
\end{eqnarray}

We can then compute $\eta(f_i, g_l)$ based on recurrence relation \ref{eq:raid:1} and dynamic programming, with $O(f \cdot g)$ time complexity and $O(f \cdot g)$ memory complexity.\\

Given $r$ racks $1,2,...,r$, denote $S(f,r)$ as the total number of instances for $k_l+p_l$ local-only RAID to survive $f$ failures to in $r$ racks, such that each rack has at least one failure.

For $S(f,r)$, we have the following recurrence relation (which is derived by considering what will happen if $r$-th rack contains $i$ failures):

\begin{eqnarray}
\begin{aligned}
  S(f,r)
  &= \sum_{\substack{1 \leq i \leq f \\ i \leq M}} \eta(i,g) \cdot T(f-i, r-1)
\end{aligned}
\label{eq:raid:3}
\end{eqnarray}

The base case is 

\begin{eqnarray}
  S(f,1) =
    \begin{cases}
      \eta(f,g)& \text{if $1 \leq f \leq M$}\\
      0 & \text{otherwise}
    \end{cases}       
\label{eq:raid:4}
\end{eqnarray}

Since we have already computed $\eta(f,g)$, we can further compute $S(f,r)$ based on recurrence relation \ref{eq:raid:3} and dynamic programming. The total time complexity $O(f \cdot (g+r)$, and total memory complexity and $O(f \cdot (g+r)$.

Here is an example implementation: \url{https://github.com/ucare-uchicago/mlec-sim/blob/main/src/theory/burst_theory.py#L97}

Therefore, the total number of survival instances in the whole system is:

\begin{eqnarray}
C_{X}^{r} \cdot S(f,r)
\label{eq:raid:5}
\end{eqnarray}

Therefore, the probability of data loss under $f$ failures on $r$ racks for RAID is:

\begin{eqnarray}
\begin{aligned}
\text{RAID data loss} = \frac{C_{X}^{r} \cdot S(f,r)} 
{C_{X}^{r} \cdot T(f,r)}
= \frac{ S(f,r)} { T(f,r)}
\end{aligned}
\label{eq:raid:6}
\end{eqnarray}



\section{Survival instances under local declustered parity}

It's similar to local clustered erasure in Section \ref{sec-raid}, but now the size of the disk group is usually larger than $n_l$. 

Suppose the size of the disk group is $D$, usually $n_l \leq D \leq Z$, where $Z$ is the size of the enclosure.

If any disk group has more than $p_l$ disk failures, then there is data loss.

So this time a rack contains $g = M/D$ disk groups.

We can then compute the data loss in the same way that we did for RAID. Therefore, the probability of data loss under $f$ failures on $r$ racks for local-only Declustered erasure is:

\begin{eqnarray}
\begin{aligned}
\text{Declustered data loss} = \frac{C_{X}^{r} \cdot S(f,r)} 
{C_{X}^{r} \cdot T(f,r)}
= \frac{ S(f,r)} { T(f,r)}
\end{aligned}
\label{eq:dp:1}
\end{eqnarray}


\section{Survival instances under network clustered erasure}

TBD, this is more challenging.

\section{Survival instances under network declustered erasure}

This is easy.

Consider $n_n=k_n+p_n$ network-only declustered erasure.

There is data loss whenever there are more than $p_n$ affected racks.

Therefore:

\begin{eqnarray}
  \text{Net-declus Data loss} =
    \begin{cases}
      1 & \text{if $r > p_n$}\\
      0 & \text{otherwise}
    \end{cases}       
\label{eq:net_dp:1}
\end{eqnarray}

where $r$ is the number of affected racks.

\section{Survival instances under MLEC clustered}

TBD

\section{Survival instances under MLEC Declustered}

TBD

\end{document}